### 2020-05-11 README.Rmd
update logo and version number
update ci pipeline

### What is New in v0.1.4.5?
This version of `areal` contains all of the bug fixes that were identified by early adaopters after the initial CRAN submission. Special thanks to [Matt Herman](https://github.com/mfherman) and [David Blodgett](https://github.com/dblodgett-usgs) for their issues and pull requests! Check out the [NEWS file](/NEWS.md) for details on all of the bugs that were identified.

>>>>

### What is New in v0.1.6?
This version contains updates under the hood to make it compatible with `dplyr`'s v1.0 release!
